Analysing Melbourne CBD pedestrian counts data with a focus on imputation methods

### 2017-10-21 thesis/draft.Rmd
WIP: removing plot titles, improving figure captions

```{r, fig.width = 8, fig.height=2, fig.cap = "Plot of simulated missingness method 2 at Bourke Street Mall (South) with 20% of the training data removed as a sequence. This method of simulating missing data is a better representation of the missing data observed at sensors with a large proportion of missing data compared to randomly removing hourly observations from the training data."}
ggplot() + geom_line(aes(x = dfa2$Date_Time, y = mall_missing_2),
                size = 0.1, alpha = 1) +
           labs(y = "Pedestrian Count", x = "Time and Date",
                title = "Simulated Missingness 2") +
          theme_minimal() + theme(plot.title = element_text(hjust = 0.5))
```

@@

```{r, fig.width = 8, fig.height=2, fig.cap = "Plot of simulated missingness method 2 at Bourke Street Mall (South) with 50% of the training data removed as a sequence. A large proportion of the training data is removed to test the robustness of the imputation method used at sensors with extremely large proportions of missing data during the training period defined."}
ggplot() + geom_line(aes(x = dfa2$Date_Time, y = mall_missing_3),
                size = 0.1, alpha = 1) +
           labs(y = "Pedestrian Count", x = "Time and Date",
                title = "Simulated Missingness 3") +
          theme_minimal() + theme(plot.title = element_text(hjust = 0.5))
```

>>>>

```{r, fig.width = 8, fig.height=2, fig.cap = "Plot of simulated missingness method 2 at Bourke Street Mall (South) with 20% of the training data removed as a sequence. This method of simulating missing data is a better representation of the missing data observed at sensors with a large proportion of missing data compared to randomly removing hourly observations from the training data."}
ggplot() + geom_line(aes(x = dfa2$Date_Time, y = mall_missing_2),
                size = 0.1, alpha = 1) +
           labs(y = "Pedestrian Count", x = "Time and Date") +
          theme_minimal() + theme(plot.title = element_text(hjust = 0.5))
```

@@

```{r, fig.width = 8, fig.height=2, fig.cap = "Plot of simulated missingness method 2 at Bourke Street Mall (South) with 50% of the training data removed as a sequence. A large proportion of the training data is removed to test the robustness of the imputation method used at sensors with extremely large proportions of missing data during the training period defined."}
ggplot() + geom_line(aes(x = dfa2$Date_Time, y = mall_missing_3),
                size = 0.1, alpha = 1) +
           labs(y = "Pedestrian Count", x = "Time and Date") +
          theme_minimal() + theme(plot.title = element_text(hjust = 0.5))
```
